Enhancement of SDR in Thessaloniki

### 2024-02-22 GHI_enh_03_process.tex
Commit 2024-02-22 14:14

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-02-19}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-448.24 -172.37  -59.22  113.90  892.70

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -1.126e+02  5.761e+01  -1.955   0.0514 .  
as.numeric(Date)  4.155e-07  4.624e-08   8.985   <2e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 244.7 on 359 degrees of freedom
Multiple R-squared:  0.1836,    Adjusted R-squared:  0.1813 
F-statistic: 80.72 on 1 and 359 DF,  p-value: < 2.2e-16
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-448.24 -172.37  -59.22  113.90  892.70

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -1.126e+02  5.761e+01  -1.955   0.0514 .  
ST_E_monthly$Date  4.155e-07  4.624e-08   8.985   <2e-16 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 244.7 on 359 degrees of freedom
Multiple R-squared:  0.1836,    Adjusted R-squared:  0.1813 
F-statistic: 80.72 on 1 and 359 DF,  p-value: < 2.2e-16
\end{verbatim}

@@

\FunctionTok{save}\NormalTok{(}\AttributeTok{file =} \FunctionTok{paste0}\NormalTok{(}\StringTok{"./data/"}\NormalTok{, }\FunctionTok{basename}\NormalTok{(}\FunctionTok{sub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{.R"}\NormalTok{, }\StringTok{".Rda"}\NormalTok{, Script.Name))),}
     \AttributeTok{list =}\NormalTok{ objects,}
     \AttributeTok{compress =} \StringTok{"xz"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
2024-02-19 10:09:06.3 athan@tyler GHI_enh_03_process.R 2.125423 mins
\end{verbatim}

>>>>

\title{Enhancement of SDR in Thessaloniki}
\author{Natsis Athanasios\footnote{Laboratory of Atmospheric Physics, AUTH, \href{mailto:natsisphysicist@gmail.com}{\nolinkurl{natsisphysicist@gmail.com}}} \and Alkiviadis Bais\footnote{Laboratory of Atmospheric Physics, AUTH}}
\date{2024-02-22}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-382.05 -149.78  -46.64   98.42  770.22

Coefficients:
                   Estimate Std. Error t value Pr(>|t|)    
(Intercept)      -1.067e+02  5.109e+01  -2.088   0.0375 *  
as.numeric(Date)  3.393e-07  4.098e-08   8.279  2.5e-15 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 216.2 on 358 degrees of freedom
Multiple R-squared:  0.1607,    Adjusted R-squared:  0.1583 
F-statistic: 68.54 on 1 and 358 DF,  p-value: 2.498e-15
\end{verbatim}

@@

Residuals:
    Min      1Q  Median      3Q     Max 
-382.05 -149.78  -46.64   98.42  770.22

Coefficients:
                    Estimate Std. Error t value Pr(>|t|)    
(Intercept)       -1.067e+02  5.109e+01  -2.088   0.0375 *  
ST_E_monthly$Date  3.393e-07  4.098e-08   8.279  2.5e-15 ***
---
Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1

Residual standard error: 216.2 on 358 degrees of freedom
Multiple R-squared:  0.1607,    Adjusted R-squared:  0.1583 
F-statistic: 68.54 on 1 and 358 DF,  p-value: 2.498e-15
\end{verbatim}

@@

\FunctionTok{cat}\NormalTok{(objects, }\AttributeTok{sep =} \StringTok{"}\SpecialCharTok{\textbackslash{}n}\StringTok{"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
aa
aday
All_daily_ratio_lim
alpha
ampl
avar
BIO_ELEVA
C1_Clearness_Kt_THRES
C1_GLB_diff_THRES
C2_Clearness_Kt_THRES
C3_cs_ref_ratio
C4_cs_ref_ratio
C4_GLB_diff_THRES
C4_lowcut_ratio
C4_lowcut_sza
Clear_daily_ratio_lim
CLEARdir
Cloud_daily_ratio_lim
cols
common_data_13
common_data_14
common_data_14_2
CS_file_13
CS_file_14
CS_file_14_2
csmodel
Daily_aggregation_N_lim
Daily_confidence_limit
daylist
Days_of_year
I1_longterm
I2_szatrend
I3_trendsconsist
ii
Input_data_ID
Kurudz_SC
MIN_ELEVA
MIN_N
Monthly_aggegation_N_lim
Monthly_confidence_limit
my.cols
my.cols.gr
pyear
R_COMPILE_PKGS
raw_input_data
running_mean_window_days
running_mean_window_years
SEAS_MIN_N
SelEnhanc
SZA_aggregation_N_lim
SZA_BIN
SZA_confidence_limit
variables_fl
yearstodo
ylim
ST_daily
ST_E_daily
ST_E_daily_seas
ST_E_monthly
ST_E_monthly_seas
ST_E_sza
ST_E_yearly
ST_extreme_daily
ST_extreme_monthly
ST_extreme_SZA
ST_extreme_yearly
ST_G0
ST_G1
ST_monthly
ST_sza
ST_total
ST_yearly
\end{verbatim}

\begin{Shaded}
\begin{Highlighting}[]
\FunctionTok{save}\NormalTok{(}\AttributeTok{file =} \FunctionTok{paste0}\NormalTok{(}\StringTok{"./data/"}\NormalTok{, }\FunctionTok{basename}\NormalTok{(}\FunctionTok{sub}\NormalTok{(}\StringTok{"}\SpecialCharTok{\textbackslash{}\textbackslash{}}\StringTok{.R"}\NormalTok{, }\StringTok{".Rda"}\NormalTok{, Script.Name))),}
     \AttributeTok{list =}\NormalTok{ objects,}
     \AttributeTok{compress =} \StringTok{"xz"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{verbatim}
2024-02-22 12:05:59.3 athan@tyler GHI_enh_03_process.R 2.189978 mins
\end{verbatim}
